---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(reactable)
library(data.table)
```

# NiceSeq {.tabset}

## PCA {.tabset}

### All peaks
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/PCA/NiceSeq/all_peaks", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Top 500 most variable peaks
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/PCA/NiceSeq/top_500", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## HM
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/HM/NiceSeq", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# H3K36me2 {.tabset}

## PCA
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/PCA/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## HM
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/HM/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# H3K27me3 {.tabset}

## PCA
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/PCA/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## HM
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/HM/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# Paired comparisons {.tabset}

## H3K36me2 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K36me2/Day_1", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K36me2/Day_5", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K36me2/Day_9", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

## H3K27me3 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K27me3/Day_1", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K27me3/Day_5", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K27me3/Day_9", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

## H3K9me3 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K9me3/Day_1", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K9me3/Day_5", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K9me3/Day_9", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

## NSD2 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/NSD2/Day_1", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/NSD2/Day_5", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/NSD2/Day_9", pattern= "*.jpeg", full.names=T)
include_graphics(imageList,dpi = 600)
```

# Genic/Intergenic Scatterplots {.tabset}

## H3K36me2
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K36me2/genic_intergenic_shading_plots", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## H3K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/paired_comparisons/K27me3/genic_intergenic_scatterplots", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# Volcano plot for PTM marks

## K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/volcano_plot/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# Genes in blue bins {.tabset}

## scatterplot
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/scatterplot", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## RNAseq
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/RNAseq", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## NSD2
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/NSD2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K27me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K36me2
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K36me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K36me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K9me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K9me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K4me1
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K4me1", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K4me3
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K4me3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27ac
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/K27ac", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# NSD2 norm counts at Vehicle Day 1 {.tabset}

## T-test
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/NSD2_norm_counts_at_baseline/t_test", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## Wilcoxon
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("/Users/padilr1/Documents/NSD2i/pushed_figs/genes_with_increased_K27me3/genes_in_blue_bins/NSD2_norm_counts_at_baseline/wilcoxon", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

# IGR heatmaps {.tabset}

## K36me2 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K36me2/D1", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K36me2/D5", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K36me2/D9", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K27me3 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K27me3/D1", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K27me3/D5", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K27me3/D9", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## K9me3 {.tabset}

### Day 1
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K9me3/D1", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 5
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K9me3/D5", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Day 9
```{r,echo = FALSE,fig.show = "hold", out.width = "60%", fig.align = "default"}
imageList <- list.files("~/Documents/NSD2i/pushed_figs/IGR_plots/K9me3/D9", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```